\vspace{-0.25em}\thetitle

### 2009-07-27 paper.tex
...

\section{Model \& Hypothesis}

@@

Our methodology for recovering the hypothesized linear structure of network traffic from trace samples uses a variety of cutting-edge and recently developed data-mining techniques.
To extract linear subspace structure, we use Ma~\emph{et~al.}'s 2007 algorithm based on lossy compression of data points~\cite{Ma07}.

@@

>>>>

\section{Model \& Hypothesis}\sec{model-hypothesis}

@@

Our experimental methodology has three parts:
training, prediction and evaluation.
For training, we take a sample of network trace traffic and try to recover the structure hypothesized in \Section{model-hypothesis} from it.
For prediction, we use the trained model to predict behaviors of a separate set of flows from the same trace, using only knowledge of a few initial packets of each.
Finally, we must evaluate the quality of these predictions.
As noted in the \Section{introduction}, due to nondeterminism we cannot possibly predict exact behaviors of flows and must instead evaluate how good a predicted distribution of possible behaviors is as compared to actual outcomes.
% One relatively intuitive measure of prediction quality we use is threshold testing.

% Our methodology for recovering the hypothesized linear structure of network traffic from trace samples uses a variety of powerful computational tools:
% \begin{enumerate}
%   \item Compute the linear representation matrix of the trace.
%   \item Perform linear subspace segmentation, extracting subspaces near which significant amounts of data points lie.
%   % For this step, we use Ma~\emph{et~al.}'s 2007 algorithm based on lossy compression of data~\cite{Ma07}.
%   \item Use \caps{SVD} to determine an approximation rank for each segmentation and an optimal approximation basis.
%   \item Compute the vertices of the intersection of each approximation subspace with the standard simplex.
%   For each subspace, all nonnegative points can be written as convex linear combinations of these vertices.
%   % For this we use Fukuda's excellent \caps{CDD}lib software for high-dimensional polyhedral computations, implementing a variety of convex hull and vertex enumeration algorithms~\cite{Avis92}.
%   \item Find optimal weights to approximate each data point from the vertices of its subspace.
% \end{enumerate}

@@

\subsection{Evaluating Prediction Quality}\sec{evaluation}
